---
title: "KTC Comparison Dashboard"

output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    orientation: columns
    vertical_layout: fill
    include:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(tidyverse)
library(viridis)
library(purrr)
library(DT)
library(plotly)
library(readxl)
library(haven)
library(ggplot2)
library(zipcodeR)
library(ggmap)
library(leaflet)
library(kableExtra)
library(crosstalk)
library(lubridate)
library(htmlwidgets)
library(gtsummary)
# reset_gtsummary_theme()
# theme_gtsummary_journal(journal="jama")
# theme_gtsummary_compact()

#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
color1 = "purple"
color2 = RColorBrewer::brewer.pal(9, "PuRd")[7]
color3  = "#1f77b4"
color4 = "forestgreen"
color5 = "#660708"
color6 = "red"
color7 = "#ba181b"
color8 = "#e5383b"
color9 = "#FDBBBC"
# 
all_data = read_csv("data/all_KI_data.csv", col_names = TRUE) %>%
  nest(WITHIN_RADIUS = matches("_WR$")) %>%
  mutate(REPORT_DATE = ymd_hms(REPORT_DATE, truncated = 3),
         REGION = as.factor(REGION),
         REGION = addNA(REGION))

# write.csv(all_data, file = "./data/all_data.csv")
# all_data = read_csv("./data/all_data.csv") %>% select(-`...1`)

# suffix = list("age","gender","demographics", "blood_type")
# 
# for (i in suffix){
#   data_path = "./data/old_data/"   # path to the data
#   files = dir(data_path, 
#               pattern = paste0("csrs_final_tables_2006_[A-Z][A-Z]_", i,".csv"))
#   assign(paste0("df_all_", i),
#          files %>%
#            map(~ read_csv(file.path(data_path, .))%>%
#                  mutate(org = str_replace(org, "HR", "Heart"),
#                         org = str_replace(org, "HL", "Heart-Lung"),
#                         org = str_replace(org, "IN", "Intestine"),
#                         org = str_replace(org, "KI", "Kidney"),
#                         org = str_replace(org, "KP", "Kidney-Pancreas"),
#                         org = str_replace(org, "LI", "Liver"),
#                         org = str_replace(org, "LU", "Lung"),
#                         org = str_replace(org, "PA", "Pancreas"))) %>%
#            reduce(rbind))
#   }

# df_all_age =
#   df_all_age %>% 
#   mutate(
#     age_category_percent = as.numeric(age_category_percent),
#     age_category = factor(age_category,
#                       levels =c("age_2_allc2","age_2_11_allc2",
#                                 "age_12_17_allc2", "age_18_34_allc2",
#                                 "age_35_49_allc2", "age_50_64_allc2",
#                                 "age_65_69_allc2", "age_70_allc2")),
#     age_category = str_replace(age_category, "age_2_allc2", "Less Than 2 Years"),
#     age_category = str_replace(age_category, "age_2_11_allc2", "2 to 11 Years"),
#     age_category = str_replace(age_category, "age_12_17_allc2", "12 to 17 Years"),
#     age_category = str_replace(age_category, "age_18_34_allc2", "18 to 34 Years"),
#     age_category = str_replace(age_category, "age_35_49_allc2", "35 to 49 Years"),
#     age_category = str_replace(age_category, "age_50_64_allc2", "50 to 64 Years"),
#     age_category = str_replace(age_category, "age_65_69_allc2", "65 to 69 Years"),
#     age_category = str_replace(age_category, "age_70_allc2", "More Than 70 Years"))

# df_all_gender = 
#   df_all_gender %>% 
#   mutate(
#     gender_category_percent = as.numeric(gender_category_percent),
#     gender_category = factor(gender_category,
#                       levels =c("female_allc2","male_allc2")),
#     gender_category = str_replace(gender_category, "female_allc2", "Female"),
#     gender_category = str_replace(gender_category, "male_allc2", "Male"))

# df_all_demographics =
#   df_all_demographics %>%
#   mutate(
#     race_category_percent = as.numeric(race_category_percent),
#     race_category = factor(race_category,
#                       levels =c("asian_allc2","african_american_allc2",
#                                 "hispanic_latino_allc2","white_allc2",
#                                 "race_other_allc2","race_unknown_allc2")),
#     race_category = str_replace(race_category, "asian_allc2", "Asian or Pacific Islander"),
#     race_category = str_replace(race_category, "african_american_allc2", "Black or African American"),
#     race_category = str_replace(race_category, "hispanic_latino_allc2", "Hispanic or Latinx"),
#     race_category = str_replace(race_category, "white_allc2", "White or Caucasian"),
#     race_category = str_replace(race_category, "race_other_allc2", "Other"),
#     race_category = str_replace(race_category, "race_unknown_allc2", "Unknown"))

# 
# df_all_blood_type =
#   df_all_blood_type %>%
#   mutate(
#     blood_type_category_percent = as.numeric(blood_type_category_percent),
#     blood_type_category = factor(blood_type_category,
#                       levels =c("blood_type_a_allc2","blood_type_b_allc2",
#                                 "blood_type_ab_allc2","blood_type_o_allc2",
#                                 "blood_type_unknown_allc2")),
#     blood_type_category = str_replace(blood_type_category, "blood_type_a_allc2", "A"),
#     blood_type_category = str_replace(blood_type_category, "blood_type_b_allc2", "B"),
#     blood_type_category = str_replace(blood_type_category, "blood_type_ab_allc2", "AB"),
#     blood_type_category = str_replace(blood_type_category, "blood_type_o_allc2", "O"),
#     blood_type_category = str_replace(blood_type_category, "blood_type_unknown_allc2", "Unknown"))

# write.csv(df_all_demographics, file = "./data/df_all_demographics.csv")
# write.csv(df_all_age, file = "./data/df_all_age.csv")
# write.csv(df_all_gender, file = "./data/df_all_gender.csv")
# write.csv(df_all_blood_type, file = "./data/df_all_blood_type.csv")

df_all_demographics = read_csv("./data/df_all_demographics.csv") %>% select(-`...1`)
df_all_age = read_csv("./data/df_all_age.csv") %>% select(-`...1`)
df_all_gender = read_csv("./data/df_all_gender.csv") %>% select(-`...1`)
df_all_blood_type = read_csv("./data/df_all_blood_type.csv") %>% select(-`...1`)

organ_race = df_all_demographics %>% distinct(org) %>% pull()
organ_age = df_all_age %>% distinct(org) %>% pull()
organ_gender = df_all_gender %>% distinct(org) %>% pull()
organ_blood_type = df_all_blood_type %>% distinct(org) %>% pull()

no_transplant_centers = 
  df_all_demographics %>% 
  distinct(entire_name) %>% 
  count() %>% 
  pull()

avg_asian = 
  df_all_demographics %>% 
  filter(race_category == 'asian_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_black = 
  df_all_demographics %>% 
  filter(race_category == 'african_american_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_latino = 
  df_all_demographics %>% 
  filter(race_category == 'hispanic_latino_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_white = 
  df_all_demographics %>% 
  filter(race_category == 'white_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_other = 
  df_all_demographics %>% 
  filter(race_category == 'race_other_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_unknown = 
  df_all_demographics %>% 
  filter(race_category == 'race_unknown_allc2') %>% 
  select(race_category_percent)%>% 
  pull() %>%
  mean(na.rm = TRUE) %>%
  round(.,1)

avg_unknown_other = 100 - sum(avg_asian, avg_black, avg_latino, avg_white)
  # df_all_demographics %>% 
  # filter(race_category == 'race_unknown_allc2' | race_category == 'race_other_allc2') %>% 
  # select(race_category_percent)%>% 
  # pull() %>%
  # mean(na.rm = TRUE) %>%
  # round(.,1)

waitlist_demo_cols = 
  c("WLC_A2_ALLC2", "WLC_A10_ALLC2", "WLC_A17_ALLC2", "WLC_A34_ALLC2", "WLC_A49_ALLC2", "WLC_A64_ALLC2",
    "WLC_GM_ALLC2", "WLC_GF_ALLC2", "WLC_RA_ALLC2", "WLC_RB_ALLC2", "WLC_RH_ALLC2", "WLC_RO_ALLC2",
    "WLC_RU_ALLC2", "WLC_RW_ALLC2", "WLC_BAB_ALLC2", "WLC_BA_ALLC2", "WLC_BB_ALLC2", "WLC_BO_ALLC2",
    "WLC_BU_ALLC2","WLC_PRA80_ALLC2", "WLC_PTXY_ALLC2","WLC_KIDIA_ALLC2", "WLC_KIGLO_ALLC2", 
    "WLC_KIHYP_ALLC2", "WLC_KIMIS_ALLC2", "WLC_KINEO_ALLC2", "WLC_KIOTH_ALLC2", "WLC_KIPOL_ALLC2",
    "WLC_KIREN_ALLC2", "WLC_KIRTR_ALLC2", "WLC_KITUB_ALLC2", "WLC_KICON_ALLC2")

ddtx_demo_cols = 
    c("RCC_A2_C", "RCC_A10_C", "RCC_A17_C", "RCC_A34_C", "RCC_A49_C", "RCC_A64_C", "RCC_GM_C", "RCC_GF_C", 
      "RCC_RA_C", "RCC_RB_C", "RCC_RH_C", "RCC_RO_C", "RCC_RU_C", "RCC_RW_C", "RCC_BAB_C", "RCC_BA_C", 
      "RCC_BB_C", "RCC_BO_C", "RCC_BMI20_C", "RCC_BMI25_C", "RCC_BMI30_C", "RCC_DIA_C", "RCC_GLO_C", "RCC_HYP_C",
      "RCC_MIS_C", "RCC_NEO_C", "RCC_OTK_C", "RCC_POL_C", "RCC_VAS_C", "RCC_RET_C", "RCC_TUB_C", "RCC_CON_C",
      "RCC_PRA80_C", "RCC_PTXY_C")

ldtx_demo_cols = str_replace(ddtx_demo_cols, "^RCC", "RCL")
ldtx_demo_cols = str_replace(ldtx_demo_cols, "_RET_", "_KIRET_")

demo_cols = c(waitlist_demo_cols, ddtx_demo_cols, ldtx_demo_cols)
demo_cols
```

Interactive Map {data-icon="ion-map"}
=====================================  

```{r include=FALSE}

# all_data = read_csv("data/all_KI_data.csv", col_names = TRUE) %>%
#   janitor::clean_names() %>%
#   select(ctr_id, entire_name, primary_city, primary_state, primary_zip, region) %>%
#   mutate(primary_zip = substr(primary_zip, 1, 5)) %>%
#   distinct() %>%
#   drop_na()
# 
# for (zipcode in all_data["primary_zip"]){
#   df_zip_geo = tibble(geocode_zip(zipcode))
# }
# 
# df_all_data = 
#   all_data %>%
#   rename(zipcode = primary_zip) %>%
#   left_join(., df_zip_geo, by = "zipcode")
# 
# write.csv(df_all_data, file = "./data/df_all_data.csv")
df_all_data = read_csv("./data/df_all_data.csv") %>% select(-`...1`)

# Wrap data frame in SharedData
sd <- SharedData$new(df_all_data)

```

Column { data-width=500 }
-------------------------------------

### Interactive map
    
```{r map}
sd %>% 
  leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$OpenStreetMap) %>% 
  leaflet::addAwesomeMarkers(
    popup = ~paste0(
      '<b>',df_all_data$entire_name, '</b>',
      '<br>',
      "Center ID: ", df_all_data$ctr_id, "",
      '<br>',
      "Region: ", df_all_data$region, "",
      '<br>',
      "City: ", df_all_data$primary_city, "",
      '<br>',
      "State: ", df_all_data$primary_state, "",
      '<br>',
      "Zip Code: ", df_all_data$zipcode, "",
      '<br>',
      "Longitude: ", df_all_data$lng, "",
      '<br>',
      "Latitude: ", df_all_data$lat, ""
    )  # end popup()
    # icon = awesomeIcons(
    #   library = "ion",
    #   icon = ifelse(
    #     test = str_detect(df$center_name, "NY"),
    #     yes = "ion-android-star-outline",
    #     no = "ion-android-radio-button-off"
    #   ),
    #   iconColor = "white",
    #   markerColor = ifelse(
    #     test = df$lng == "-74", 
    #     yes = "red",
    #     no = "blue"
    #   )
    # )
  ) %>%   # end addAwesomeMarkers()
  leaflet::addMeasure()
```

Column  { data-width=500 }
-------------------------------------
### Filters

```{r filters}

filter_select(
  id = "center",
  label = "Center Name",
  sharedData = sd,
  group = ~entire_name
  )

filter_select(
  id = "zipcode",
  label = "Zip Code",
  sharedData = sd,
  group = ~zipcode
  )

filter_slider(
    id = "zipradius",
    label = "Radius",
    sharedData = sd,
    column = ~region,
    step = 1,
    round = TRUE,
    sep = "",
    ticks = FALSE,
    width = "50%")

filter_checkbox(
    id = "region",
    label = "Region",
    columns = 3,
    sharedData = sd,
    group = ~region
  )
```

### Datatable

```{r datatable}

sd %>%
  datatable(
    filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons",  # add download buttons, etc
      "Scroller"  # for scrolling down the rows rather than pagination
    ),
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    class = "compact",
    width = "100%",
    options = list(
      dom = "Blrtip",  # specify content (search box, etc)
      deferRender = TRUE,
      scrollY = 300,
      scroller = TRUE,
      columnDefs = list(
        list(
          visible = FALSE,
          targets = c(2, 3, 5:15)
        )
      ),
      buttons = list(
        I("colvis"),  # turn columns on and off
        'copy', 
        'print',
        list(extend = 'collection',
             buttons = c('csv', 'excel', 'pdf'),
             text = 'Download')
      )
    ),
    colnames = c(
      "Center ID" = "ctr_id",
      "Center Name" = "entire_name",
      "Region" = "region",
      "Primary City" = "primary_city",
      "Primary State" = "primary_state",
      "Zip Code" = "zipcode",
      "Longitude" = "lng",
      "Latitude" = "lat"
    )
  )
```

Patient Demographics {data-icon="ion-android-people"}
===================================== 

Column { data-width=175 }
-----------------------------------------------------------------------

### Transplant Centers {.value-box}
```{r}
valueBox(value = paste(format(no_transplant_centers, big.mark = ","), "", sep = " "), 
         caption = "Total transplant centers", 
         icon = "fas fa-hospital", 
         color = "#fde725"
)
```

### Number of Recipients {.value-box}
```{r}
valueBox(value = paste(format('22K', big.mark = ","), "", sep = " "), 
         caption = "Number of transplant recipients in 2018", 
         icon = "fas fa-users", 
         color = "#a0da39")
```

### Number on Waiting List {.value-box}
```{r}
valueBox(value = paste(format('785K', big.mark = ","), "", sep = " "), 
         caption = "Number of patients on waiting list in 2018", 
         icon = "fas fa-users", 
         color = "#4ac16d")
```

### Percent Asian {.value-box}
```{r}
valueBox(value = paste(format(avg_asian, big.mark = ","), "%", sep = " "), 
         caption = paste0("Percent of recipients who identify as",'<br>',"Asian/Pacific Islander"), 
         icon = "fas fa-procedures", 
         color = "#1fa187")
```

### Percent Black {.value-box}
```{r}
valueBox(value = paste(format(avg_black, big.mark = ","), "%", sep = " "), 
         caption = paste0("Percent of recipients who identify as",'<br>',"Black/African American"), 
         icon = "fas fa-procedures", 
         color = "#277f8e")
```

### Percent Latino {.value-box}
```{r}
valueBox(value = paste(format(avg_latino, big.mark = ","), "%", sep = " "), 
         caption = paste0("Percent of recipients who identify as",'<br>',"Latinx/Hispanic"), 
         icon = "fas fa-procedures", 
         color = "#365c8d")
```

### Percent White {.value-box}
```{r}
valueBox(value = paste(format(avg_white, big.mark = ","), "%", sep = " "), 
         caption = paste0("Percent of recipients who identify as",'<br>',"White/Caucasian"), 
         icon = "fas fa-procedures", 
         color = "#46327e")
```

<!-- ### Percent Other {.value-box} -->
<!-- ```{r} -->
<!-- valueBox(value = paste(format(avg_other, big.mark = ","), "%", sep = " "),  -->
<!--          caption = "Percent of recipients of other race/ethnicity",  -->
<!--          icon = "fas fa-procedures",  -->
<!--          color = "#440154") -->
<!-- ``` -->
Column {.tabset}
-------------------------------------

### Age Group by Zip Code and Organ Type

Scatter plots of age by zipcode, with a facet wrap by organ type.

```{r age_by_zip, warning=FALSE}
phrase = "SRTR Multiorgan Transplant Data, August 2020 Release"

plot = 
  df_all_age %>% 
  ggplot(aes(x = zipcode, y = age_category_percent, color = age_category)) + 
  geom_point() + 
  labs(
      # title = "Patient Age Groups by Zipcode",
      #  subtitle = phrase,
       x = "Zipcode",
       y = "Age Group (Percent)",
       color = "Age Group") + 
  theme_minimal() + 
  theme(axis.text.x=element_text(angle=90, hjust=1)) + 
  scale_color_hue(labels = c("Less Than 2 Years", "2 to 11 Years", 
                             "12 to 17 Years", "18 to 34 Years", 
                             "35 to 49 Years", "50 to 64 Years", 
                             "65 to 69 Years", "More Than 70 Years")) + 
  facet_wrap(~org)

fig <- ggplotly(plot) %>% layout(legend = list(orientation = 'h'))
fig
```

### Gender by Zip Code and Organ Type

Scatter plots of gender by zipcode, with a facet wrap by organ type.

```{r gender_by_zip, warning=FALSE}

plot = 
  df_all_gender %>% 
  ggplot(aes(x=zipcode, y =gender_category_percent, color = gender_category)) + 
  geom_point()+ 
  labs(
    # title = "Patient Gender by Zipcode", 
    #    subtitle = phrase,
       x = "Zipcode",
       y = "Gender (Percent)", color = "Gender"
  ) + 
  theme_minimal() + 
  theme(axis.text.x=element_text(angle=90, hjust=1)) + 
  scale_color_hue(labels = c("Female", "Male")) + 
  facet_wrap(~org)

fig <- ggplotly(plot) %>% layout(legend = list(orientation = 'h'))
fig
```

### Race/Ethnicity by Zip Code and Organ Type

Scatter plots of race by zipcode, with a facet wrap by organ type.

```{r race_by_zip, warning=FALSE}
plot = 
  df_all_demographics %>% 
  ggplot(aes(x=zipcode, y =race_category_percent, color = race_category)) + 
  geom_point() + 
  theme_minimal() + 
  labs(
    # title = "Patient Demographics by Zipcode", 
    # subtitle = phrase,
    x = "Zipcode",
    y = "Race (Percent)", 
    color = "Race") + 
  scale_color_hue(labels = c("African American", "Asian", "Hispanic or Latino", 
                             "Other", "Unknown", "White")) + 
  theme(axis.text.x=element_text(angle=90, hjust=1)) + 
  facet_wrap(~org)


fig <- ggplotly(plot) %>% layout(legend = list(orientation = 'h'))
fig
```

### Blood Type by Zip Code and Organ Type

Scatter plots of blood type by zipcode, with a facet wrap by organ type.

```{r bloodtype_by_zip, warning=FALSE}
plot = 
  df_all_blood_type %>%
  ggplot(aes(x = zipcode, y = blood_type_category_percent, color = blood_type_category)) + 
  geom_point() + 
  labs(
    # title = "Patient Blood Types by Zipcode", 
    #    subtitle = "SRTR Kidney Transplant Data, August 2020 Release",
       x = "Zipcode",
       y = "Blood Type (Percent)", color = "Blood Type") + 
  theme_minimal() + 
  scale_color_hue(labels = c("A", "AB", "B", "O", "Unknown")) + 
  theme(axis.text.x=element_text(angle=90, hjust=1)) + 
  facet_wrap(~org)

fig <- ggplotly(plot) %>% layout(legend = list(orientation = 'h'))
fig
```


Organ Offer Acceptance Practices {data-icon="ion-medkit"}
=====================================  

Column {.tabset}
-------------------------------------

### Offer acceptance over time, by region

<!-- We plotted offer/acceptance ratios (O/A) over time at all centers, organized by the 11 OPTN regions. This data was not available prior to 2017. The offer/acceptance ratio is calculated based on offer/acceptance ratios for all centers in the country. A value > 1 indicates that a center is more likely to accept an organ compared to other centers in the country. -->

<!-- Transplant centers missing O/A information were excluded from the plots below. Generally speaking, O/A ratios have remained stable over time across regions, although the large amount of data makes it difficult to compare in this context. -->

Change in offer acceptance hazard ratios over time, by region

```{r OA_over_time, warning = FALSE}
oa_v_time = all_data %>%
  filter(!is.na(OA_OVERALL_HR_MN_CENTER)) %>%
  select(CTR_ID, REGION, REPORT_DATE, OA_OVERALL_HR_MN_CENTER)  %>%
  group_by(REGION) %>%
  mutate(CTR_COLOR_TYPE = dense_rank(x = CTR_ID)) %>%
  ggplot(aes(x = REPORT_DATE, y = OA_OVERALL_HR_MN_CENTER, color = factor(CTR_COLOR_TYPE))) +
  geom_point(show.legend = FALSE, alpha = 0.5) +
  geom_path(show.legend = FALSE, alpha = 0.5) +
  facet_wrap(~REGION,) + 
  labs(y = "Offer Acceptance Ratios \n(compared to National O/A)", 
       x = "Year",
       title = "Offer Acceptance Ratios over Time, by OPTN Region")


fig <- ggplotly(oa_v_time) %>% layout(legend = list(orientation = 'h'))
fig
```

### Offer acceptance over time, by state

<!-- For NY specific transplant centers, we can see that only 4 transplant centers had O/As < 1. NYU Medical Center (NYUCTX1) had a large increase in its O/A in the last year, while SUNY Upstate (NYUMTX1) has had a gradual decline in its O/A since 2017.  -->

```{r NY_OA_over_time, warning = FALSE}
ny_oa_v_time = 
  all_data %>%
  filter(!is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REGION, REPORT_DATE, OA_OVERALL_HR_MN_CENTER)  %>%
  ggplot(aes(x = REPORT_DATE, y = OA_OVERALL_HR_MN_CENTER, color = CTR_ID)) +
  geom_point(show.legend = TRUE) +
  geom_path() + 
  labs(y = "Offer Acceptance Ratios \n(compared to National O/A)", 
       x = "Year",
       title = "Offer Acceptance Ratios over Time, in NY State",
       colors = "Center ID")

fig <- ggplotly(ny_oa_v_time) %>% layout(legend = list(orientation = 'h'))
fig
```

Time to Transplant {data-icon="ion-ios-timer"}
=====================================  

<!-- The median time to transplant for patients on NY transplant center kidney wait lists has generally decreased since 2017, although this is not consistent across all centers. -->

Column  {.tabset}
-------------------------------------

### Median Time to Transplant 

``` {r ttt_v_time}
ttt_cols = c("TTT_25_C", "TTT_50_C", "TTT_75_C")
ttt_v_time = all_data %>%
  filter(!is.na(TTT_50_C) & !is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REGION, REPORT_DATE, OA_OVERALL_HR_MN_CENTER, TTT_50_C)%>%
  group_by(REPORT_DATE) %>%
  ggplot(aes(x = REPORT_DATE, y = TTT_50_C, color = CTR_ID)) +
  geom_point() +
  geom_line() + 
  labs(y = "Median Time to Transplant (months)", 
       x = "Year",
       title = "Median Time to Transplant (months) in NY State",
       colors = "Center ID") +
  theme(legend.position = "right") + 
  guides(color = guide_legend(ncol = 1))
  #facet_wrap( ~ as.Date(REPORT_DATE), scales = 'free')

fig <- ggplotly(ttt_v_time) %>% layout(legend = list(orientation = 'h'))
fig
```

Transplant Rate vs. O/A Ratios over Time {data-icon="ion-stats-bars"}
=====================================  

Column  {.tabset}
-------------------------------------

### Transplant Rate vs. O/A Ratios Over Time by State 

<!-- When looked at as a whole over time, we might infer that since 2019, the transplant rate has increased with decreasing O/As over time, indicated by the relatively increasing slope of a best-fit line across centers. However, this inference is not well supported-- this method is very sensitive to outliers given the small sample size. -->

``` {r txrate_v_oa_v_time}
txrate_v_oa_v_time = all_data %>%
  filter(!is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REPORT_DATE, OA_OVERALL_HR_MN_CENTER, TMR_TXR_C2) %>%
  arrange(REPORT_DATE) %>%
  ggplot(aes(x = OA_OVERALL_HR_MN_CENTER, y = TMR_TXR_C2)) +
  geom_point(aes(color = CTR_ID)) +
  geom_smooth(method = lm, se = FALSE, show.legend = FALSE,  linetype = "dashed", size = 0.5, alpha = 0.5) +
  facet_wrap( ~ as.Date(REPORT_DATE), scales = 'free') +
  labs(
    x = "Offer/Acceptance Ratio",
    y = "Transplant Rate (per person years)",
    colors = "Center ID"
  )

fig <- ggplotly(txrate_v_oa_v_time) %>% layout(legend = list(orientation = 'h'))
fig
```

