---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Question 1:

How do centers vary by geography:
- offer acceptance ratios
- who gets added/death while on waitlist
- association btwn willingness to accept high-risk pts (e.g., based on kidney donor risk index, donor creatinine, hep C status) and time to transplant?

question 2:
- Have centers changed their practices over time?

Question 3:
- What center-related features are associated with higher/riskier offer acceptance ratios?




Show comparisons between different regions (have a slider for mile radius perhaps based on zipcode?)


want a dashboard like this with multiple centers:
https://www.srtr.org/transplant-centers/ny-presbyterian-hospitalcolumbia-univ-medical-center-nycp/?organ=kidney&recipientType=adult


data needed for kidney transplants:
- zip code of center
- organ risk score
- donor risk score
- waiting list length
- average duration of time on wait list
- average age of transplant recipients who died
- average age of transplant recipients who lived
- most common comorbidity?
- offer acceptance ratio over time


A. Program Summary
B. Waiting List Information 
C. Transplant Information



Understanding the Kidney tables:



The Program Summary is a one-page summary highlighting characteristics of the program, including the 
number of candidates on the waiting list, 
the number of transplants performed at the program, 
the number of patients being cared for by the program, 
and patient outcomes, 
  including outcomes while on the waiting list (the transplant rate and the death rate while on the waiting list) and 
  outcomes after transplant (patient and graft survival probabilities). 
  
survival probabilities for adults and children (pediatrics) are provided separately. 

For each of the outcomes measures presented, a comparison is provided showing what would be expected at this program if it were performing as similar programs around the country perform when treating similar patients. 

More details regarding these outcome measures are provided in Sections B and C of the report.


Levels of analysis
- program
- mi radius/city
- region
- national

REGIONS FROM OPTN
Region 1: Connecticut, Maine, Massachusetts, New Hampshire, Rhode Island, Eastern Vermont
Region 2: Delaware, District of Columbia, Maryland, New Jersey, Pennsylvania, West Virginia, Northern Virginia
Region 3: Alabama, Arkansas, Florida, Georgia, Louisiana, Mississippi, Puerto Rico
Region 4: Oklahoma, Texas
Region 5: Arizona, California, Nevada, New Mexico, Utah
Region 6: Alaska, Hawaii, Idaho, Montana, Oregon, Washington
Region 7: Illinois, Minnesota, North Dakota, South Dakota, Wisconsin
Region 8: Colorado, Iowa, Kansas, Missouri, Nebraska, Wyoming
Region 9: New York, Western Vermont
Region 10: Indiana, Michigan, Ohio
Region 11: Kentucky, North Carolina, South Carolina, Tennessee, Virginia

```{r grab_data}
# for file in data file aka year
# read in csv spec sheets
# mutate and make tidy, one var per column

```

Table combining the following:
center info
center zip code (from address)
center region (from OPTN data)

