---
title: "Plot  Drafts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, collapse = TRUE)
library(tidyverse)
library(lubridate)
```

First plot is offer acceptance ratios by center... will need to reduce number included in plot

```{r load_data}

all_data = read_csv("data/all_KI_data.csv", col_names = TRUE) %>%
  nest(WITHIN_RADIUS = matches("_WR$")) %>%
  mutate(REPORT_DATE = ymd_hms(REPORT_DATE, truncated = 3),
         REGION = as.factor(REGION),
         REGION = addNA(REGION))

subset_test = tail(all_data, 20)
```


## Need to separate out the age group, race, and blood type variables
## naming patern is [stat_type]_[info_type][var_val]_[year_qualifier]

stat_type = WLC for waitlist, RLC for living donor tranpslant recipients, RCC for deceased donor recipients
info_type = A for age group, B for blood type, R for race, G for gender, KI for primary disease (only on waitlist), or a 3 letter code for primary disease for tx recipients
var_val = the actual information, for example A2 is age <2, A10 is age 2-11, etc, RB is Black, GF is female, BAB is blood type AB
year_qualifier can be removed, its all of the characters after the 2nd _ (ex in WLC_A2_ALLC2, the qualifier is ALLC2)

``` {r stacked_bars}


# regex functions for later

# get_col_cats = function(pattern, desc, df = all_data) {
#   cat_cols = df %>%
#     select(matches(pattern)) %>%
#     names()
#   
#   return(cat_cols)
# }
# 
# get_cat_type = function(category, col_cats) {
#   for (col_cat %in% col_cats){
#     if (category %in% col_cat)
#   }
#   
# 
# age_cols = map("[A-Z]{3}_A[1-9]", ~ get_col_cats(pattern = .x))
# gender_cols = map("^WLC_G[FM]|^RC[CL]_G[FM]", ~ get_col_cats(pattern = .x))
# race_cols = map("^WLC_R[A-Z]_|^RC[CL]_R[A-Z]_", ~ get_col_cats(pattern = .x))


waitlist_demo_cols = c("WLC_A2_ALLC2", "WLC_A10_ALLC2", "WLC_A17_ALLC2", "WLC_A34_ALLC2", "WLC_A49_ALLC2", "WLC_A64_ALLC2", "WLC_A65P_ALLC2", "WLC_A69_ALLC2", "WLC_A70P_ALLC2", "WLC_GM_ALLC2", "WLC_GF_ALLC2", "WLC_RA_ALLC2", "WLC_RB_ALLC2", "WLC_RH_ALLC2", "WLC_RO_ALLC2", "WLC_RU_ALLC2", "WLC_RW_ALLC2", "WLC_BAB_ALLC2", "WLC_BA_ALLC2", "WLC_BB_ALLC2", "WLC_BO_ALLC2", "WLC_BU_ALLC2","WLC_PRA80_ALLC2", "WLC_PTXY_ALLC2", "WLC_KIDIA_ALLC2", "WLC_KIGLO_ALLC2", "WLC_KIHYP_ALLC2", "WLC_KIMIS_ALLC2", "WLC_KINEO_ALLC2", "WLC_KIOTH_ALLC2", "WLC_KIPOL_ALLC2", "WLC_KIREN_ALLC2", "WLC_KIRTR_ALLC2", "WLC_KITUB_ALLC2", "WLC_KICON_ALLC2")

ddtx_demo_cols = c("RCC_A2_C", "RCC_A10_C", "RCC_A17_C", "RCC_A34_C", "RCC_A49_C", "RCC_A64_C", "RCC_A65P_C", "RCC_A69_C", "RCC_A70P_C", "RCC_GM_C", "RCC_GF_C", "RCC_RA_C", "RCC_RB_C", "RCC_RH_C", "RCC_RO_C", "RCC_RU_C", "RCC_RW_C", "RCC_BAB_C", "RCC_BA_C", "RCC_BB_C", "RCC_BO_C", "RCC_DIA_C", "RCC_GLO_C", "RCC_HYP_C", "RCC_MIS_C", "RCC_NEO_C", "RCC_OTK_C", "RCC_POL_C", "RCC_VAS_C", "RCC_RET_C", "RCC_TUB_C", "RCC_CON_C", "RCC_PRA80_C", "RCC_PTXY_C")

ldtx_demo_cols = str_replace(ddtx_demo_cols, "^RCC", "RCL")
ldtx_demo_cols = str_replace(ldtx_demo_cols, "_RET_", "_KIRET_")

demo_cols = c(waitlist_demo_cols, ddtx_demo_cols, ldtx_demo_cols)

as_tibble(demo_cols) %>%
  filter(str_detect(value, pattern = age_pats)) %>%
  mutate(new_val = str_sub(value, 5,-1)) %>%
  mutate(new_val = str_replace(new_val, "_[AC].*$", ""),
         age_grp = unlist(lapply(new_val, function(x) age_grps[x])))

str_replace(str_sub("WLC_A2_ALLC2", 5, -1), "_[AC].*$", "")
  
  
age_pats = c("A2", "A10", "A17", "A34", "A49", "A64", "A65P", "A69", "A70P")
age_grps = c("Age <2", "Age 2-11", "Age 12-17", "Age 18-34", "Age 35-49", "Age 50-64", "Age >65", "Age 65-69", "Age 70+" )
names(age_grps) = age_pats

race_pats = c("RA", "RB", "RH", "RO", "RU", "RW")
race_grps = c("Race Asian", "Race Black", "Ethnicity Hispanic", "Race Other", "Race Unknown", "Race White")
names(race_grps) = race_pats


dz_pats = c("DIA", "GLO", "HYP", "MIS", "NEO", "OTK", "POL", "VAS", "RET", "TUB", "CON")
dz_pats = c(dz_pats, c(paste("KI",dz_pats, sep = "")))
dz_grps = c("Dz: Diabetes", "Dz: Glomerular", "Dz: Hypertension", "Dz: Missing", "Dz: Neoplasms", "Dz: Other", "Dz: Polycystic", "Dz: Vascular", "Dz: Retransplant", "Dz: Tubular/Interstial", "Dz: Genetic")
dz_grps = c(dz_grps, dz_grps)
names(dz_grps) = dz_pats

demographic_props = all_data %>%
  filter(year(REPORT_DATE) == 2021) %>%
  select(CTR_ID, REGION, REPORT_DATE, PRIMARY_STATE, any_of(demo_cols)) %>%
  pivot_longer(cols = demo_cols, names_to = c("CATEGORY"), values_to = c("CATEGORY_PROP")) %>%
  mutate(ORG_TYPE = 
           as.factor(ifelse(str_sub(CATEGORY,1,3) == "WLC", "waitlist", 
                            ifelse(substr(CATEGORY, 3,3) == "L", "living", "deceased"))),
         CAT_TYPE = "",
         CAT_TYPE = ifelse(str_detect(CATEGORY, "^WLC_A[1-9]|^RC[CL]_A[1-9]"), "Age Group", CAT_TYPE),
         CAT_TYPE = ifelse(str_detect(CATEGORY, "^WLC_G[FM]|^RC[CL]_G[FM]"), "Gender", CAT_TYPE),
         CAT_TYPE = ifelse(str_detect(CATEGORY, "^WLC_R[A-Z]_|^RC[CL]_R[A-Z]_"), "Race", CAT_TYPE),
         CAT_TYPE = ifelse(str_detect(CATEGORY, "^WLC_B[ABOU]|^RC[CL]_B[ABOU]"), "Blood Type", CAT_TYPE),
         CAT_TYPE = if_else(str_detect(CATEGORY, "[A-Z]{3}_P[RT][AX]"), "High Ab Risk", CAT_TYPE), 
         CAT_TYPE = if_else((CAT_TYPE == "") & (str_detect(CATEGORY, "^WLC_KI|^RC[CL]_.{3}_|^RC[CL]_KI")), "Primary Disease", CAT_TYPE)) %>%
  mutate(
    CATEGORY = if_else(CAT_TYPE == "Age Group", 
    unlist(lapply(str_replace(str_sub(CATEGORY, 5, -1), "_[AC].*$", ""), function(x) age_grps[x])), CATEGORY),
    CATEGORY = if_else(CAT_TYPE == "Gender", if_else(str_sub(CATEGORY,6,6) == "M", "Gender: Male", "Gender: Female"), CATEGORY),
    CATEGORY = if_else(CAT_TYPE == "Race", 
    unlist(lapply(str_replace(str_sub(CATEGORY, 5, -1), "_[AC].*$", ""), function(x) race_grps[x])), CATEGORY),
    CATEGORY = ifelse(CAT_TYPE == "Blood Type", paste("Blood Type", str_replace(str_sub(CATEGORY, 6, -1), "_[AC].*$", "")), CATEGORY),
    CATEGORY = ifelse(CAT_TYPE == "High Ab Risk", if_else(CATEGORY == "RCC_PRA80_C", "Ab Risk: Peak PRA >= 80%", "Ab Risk: Retransplant"), CATEGORY),
    CATEGORY = if_else(CAT_TYPE == "Primary Disease", 
    unlist(lapply(str_replace(str_sub(CATEGORY, 5, -1), "_[AC].*$", ""), function(x) dz_grps[x])), CATEGORY)) %>%
  mutate(CAT_TYPE = as.factor(CAT_TYPE),
         CATEGORY = as.factor(CATEGORY)) %>%
  group_by(CTR_ID, ORG_TYPE, CAT_TYPE, CATEGORY) %>%
  filter(!is.na(CATEGORY_PROP))


demographic_props %>%
  filter(PRIMARY_STATE == "NY" & CAT_TYPE == "Age Group") %>%
  group_by(CTR_ID, ORG_TYPE, CATEGORY) %>%
  ggplot(aes(fill = CATEGORY, y = CATEGORY_PROP, x = ORG_TYPE)) +
  geom_bar(position = "stack", stat = "identity", show.legend = TRUE) +
    #geom_bar(position = "stack", stat = "identity", show.legend = FALSE) +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(x = "Center ID",
       y = "Proportion (%)",
       colors = "Age Group") +
  facet_wrap(~CTR_ID, nrow = 3)


# in one plot with facets, not great colors
# demographic_props %>%
#   filter(CTR_ID == "NYCPTX1") %>%
#   group_by(ORG_TYPE, CAT_TYPE) %>%
#   ggplot(aes(fill = factor(CATEGORY), y = CATEGORY_PROP, x = ORG_TYPE)) +
#   geom_bar(position = "stack", stat = "identity", show.legend = TRUE) +
#     #geom_bar(position = "stack", stat = "identity", show.legend = FALSE) +
#   scale_y_continuous() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
#   labs(x = "Waitlist or Organ Type",
#        y = "Proportion (%)") +
#   facet_wrap(~CAT_TYPE, nrow = 2)

```

``` {r ttt_v_time}
ttt_cols = c("TTT_25_C", "TTT_50_C", "TTT_75_C")
all_data %>%
  filter(!is.na(TTT_50_C) & !is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REGION, REPORT_DATE, OA_OVERALL_HR_MN_CENTER, TTT_50_C)%>%
  group_by(REPORT_DATE) %>%
  ggplot(aes(x = REPORT_DATE, y = TTT_50_C, color = CTR_ID)) +
  geom_point() +
  geom_line() + 
  labs(y = "Median Time to Transplant (months)", x = "Year")
  #facet_wrap( ~ as.Date(REPORT_DATE), scales = 'free')

```

``` {r ttt_v_time}
ttt_cols = c("TTT_25_C", "TTT_50_C", "TTT_75_C")
all_data %>%
  filter(!is.na(TTT_50_C) & !is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REGION, REPORT_DATE, OA_OVERALL_HR_MN_CENTER, TTT_50_C)%>%
  group_by(REPORT_DATE) %>%
  ggplot(aes(x = REPORT_DATE, y = TTT_50_C, color = CTR_ID)) +
  geom_point() +
  geom_line()
  #facet_wrap( ~ as.Date(REPORT_DATE), scales = 'free')

```

``` {r txrate_v_oa_v_time}
txrate_v_oa_v_time = all_data %>%
  filter(!is.na(OA_OVERALL_HR_MN_CENTER) & PRIMARY_STATE == "NY") %>%
  select(CTR_ID, REPORT_DATE, OA_OVERALL_HR_MN_CENTER, TMR_TXR_C2) %>%
  arrange(REPORT_DATE) %>%
  ggplot(aes(x = OA_OVERALL_HR_MN_CENTER, y = TMR_TXR_C2, color = CTR_ID)) +
  geom_point() +
  facet_wrap( ~ as.Date(REPORT_DATE), scales = 'free')

txrate_v_oa_v_time
```
# Variables for viz

*unique identifiers*:

CTR_ID, REPORT_DATE

*Offer/acceptance hazard ratio* (center compared to center, >1 is more offers than acceptances compared to ALL centers in the country for that year)

OA_OVERALL_HR_MN_CENTER

*For stratified KDRIs:*
OA_LOWRISK_HR_MN_CENTER

OA_MEDIUMRISK_HR_MN_CENTER

OA_HIGHRISK_HR_MN_CENTER

OA_HARDTOPLACE100_HR_MN_CENTER


*For map:*
transplant rate
TMR_TXR_C2

Total number of transplants in 1y(deceased and living donor, respectively)
sum(WLA_REMTXC_NC2 + WLA_REMTXL_NC2)


PRIMARY_ZIP | center zip code

*if you need to add more info like lat/long, use the zipRadius package, input the zip code, extract the lat/long*
